Constraining Black Hole Growth with High-z Quasar Observations

### 2022-09-03 ms.tex
version0903; revision 1st roll following k0901

\vspace{2mm}
\section{Results}\label{sec:result}

\vspace{2mm}
\subsection{Fitting Results}\label{sec:fitting_result}

@@

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{fits_MF.png}
\caption{
The BH mass function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
For comparison, the BHMF inferred by \citetalias{2010AJ....140..546W} is overlaid (blue curve and shaded region).
The data is used for the model parameter fitting.
%.The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
% error of observation
}
\label{fig:fitmf}
\end{figure*}

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{fits_LF.png}
\caption{
The unobscured quasar luminosity function at $z=6$ with the best-fit parameters (black solid line) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
The upper bound of faint quasar number density is derived from the cumulative QLF presented in \citet{2022NatAs...6..850J}.
The X-ray QLF data in the faint end inferred from the $z\sim 5-6.1$ quasar sample in \citet{2019ApJ...884...19G} are denoted by orange symbols,
note that we conduct an extrapolation with quasar number densities scaling with $10^{-0.72\Delta z}$ at $z$ in $5-6$ \citep{2016ApJ...833..222J}.
For comparison, we show the intrinsic QLF predicted by our model in dashed lines.
}
\label{fig:fitlf}
\end{figure*}

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{tau.png}
\caption{
The BH mass function (left) and quasar luminosity function (right) at $z=$ 6 in the case of $\fseed=0.01$, 
with different values of $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively.
Note that the other parameters are fixed to the best-fit values. 
The $z=6$ BHMF (\citetalias{2010AJ....140..546W}) and QLF (\citetalias{2018ApJ...869..150M}) 
are overlaid with the blue curve and data points.
With shorter (longer) timescales of each accretion episode $\tlife$, the number of BHs at the high mass end and bright end is under(over)-produced.
%Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
%The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
%With $\tlife$ values different from the best-fit value, the consequent QLF show 
%similar trends of deviation from observation as in the BHMF curves.
Multiple accretion bursts in each duration of $\tau \simeq 20$ Myr best produce the observations,
which is nearly half of the $e$-folding time of the exponential BH mass growth.
}
\label{fig:tau}
%\vspace{4mm}
\end{figure*}

\vspace{2mm}
\subsection{Model dependence}\label{sec:modep}
As described in \S~\ref{sec:model}, we introduce the parameter $\tau$ as a typical timescale
for individual durations of quasar accretion activity.
Specifically, we assign an Eddington ratio $\lambda$ following the ERDF for all BHs in each cycle
with a time duration of $\tau$.
Variable accretion episodes in every cycle essentially modify the effective ERDF in the whole BH growth history,
because multiple sampling of $\lambda$ reduces the possibility of a BH growing with $\lambda \gtrsim \lambda_0$
compared to that with a single sampling of $\lambda$.
%However at any time during growth, the ERDF of the BH population remains the same as at $z\sim$ 6,
%therefore we ensure treating all cosmic time equally.
In what follows, we demonstrate the role of $\tlife$ in shaping the BHMF evolution and the consequent QLF.
% tau极端小，则非常小的lambda，不能解释 （且delta func？ 有必要说或是放在后面讨论？）

\vspace{2mm}
\section{Cosmological evolution of BH mass and quasar luminosity function}\label{sec:cosm}
%\red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
%Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
%Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{BHMF_rhoz1.png}
\caption{
\if0
{\it Left panel}: BH mass functions at $z=6-10$. 
The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
evaluated by the integration of the BHMF shown in the left panel.
The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
\fi
}
\label{fig:BHMF_rhoz}
\vspace{4mm}
\end{figure*}

Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
us to probe the statistical aspect of BH evolution at higher redshifts.
As a fiducial case, we take the best-fit parameters of BH growth for our $\fseed=$ 0.01 model,
where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
We apply the result to construct BHMFs and QLFs at higher redshifts and give implications for
the future explorations of high-$z$ quasars.

\subsection{Black hole mass function}

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show our predictions of the BHMFs at five different redshifts of $z=6-10$,
with both cases of $\fseed=0.1$ and 0.01.
The seed BH mass function is already established with $M_\bullet \lesssim 2\times10^5~\Msun$ earlier than $z\sim 17$,
so the BHMF at mass ranges higher than the typical seed mass is grown from a portion of $\fseed$ of all seeds.
Therefore, with $\fseed=0.1$, the number of growing seeds is 10 times higher than in the $\fseed =0.01$ case,
which is partially reflected by the difference of BHMFs at $M_\bullet \sim 10^{5-6}~\Msun$ in their early growth.
As for $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
in all redshift bins, the BHMFs can be characterized with a double power-law function,
similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
Toward lower redshifts, the number density of BHs in the high-mass tail increases
and SMBHs with $M_\bullet \gtrsim 10^9~\Msun$ emerge owing to efficient growth of the massive BH population.
Constrained by the \citetalias{2010AJ....140..546W} BHMF with $M_\bullet \sim 10^8-3\times 10^9~\Msun$ at $z=6$, 
the two $\fseed$ cases produce similar BHMF at in this mass and redshift range (see \S~\ref{sec:fitting_result}),
while in the low mass range ($M_\bullet \lesssim 10^7~\Msun$), the difference in the two BHMF shapes is profound.
The difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
i.e., the typical masses which dominate the cumulative mass density
(see \S~\ref{sec:fitting_result}). In the case of $\fseed=0.01$, this typical mass range is higher,
despite the integrated mass density is lower than that with $\fseed=0.1$.

In the right panel of Fig.~\ref{fig:BHMF_rhoz}, 
we also present the evolution of BH cumulative mass density in a comoving volume,
defined by the integration of the BHMF as
%
\begin{equation}
 \rho_\bullet(z)=\int_{\mathcal{D}}^{} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh,
\end{equation}
%
where the mass ranges are $\mathcal{D} = M_{\bullet}<10^6$,
$10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$.
% Varying the mass ranges as $\mathcal{D} = [,10^5]$, $[10^5,10^6]$, $[10^6,10^8]$, and $[10^8,]~\Msun$,
% Varying the mass ranges as $\mathcal{D} = \{M_{\bullet}<10^5\}, \{M_{\bullet} \rm{in} 10^{5-6}\}, 
% 10^{6-8}$, and $M_{\bullet}>10^8~\Msun$,
The mass density predicted by the $\fseed=0.1$ case is overall higher than that with $\fseed=0.01$.
However, with $\fseed=0.01$, BHs in the low mass range quickly evolve into higher masses, 
leading to convergent results in the two cases at $z\sim 6$.
For comparison, we overlay the results of BH mass density evolution with $10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$
from cosmological simulations in \citet{2022MNRAS.513..670N}, with the dashed-dotted line and square colored according to the mass ranges.
At lower redshifts $z\lesssim 7$, our results are in overall good agreement with theirs.
However, our models predict more $10^{6-8}~\Msun$ BHs emerging at $z\sim 10-8$,
owing to the joint effect of our seeding scenario and growth model,
the former produces BH seeds earlier than their stringent seeding criteria,
and the latter allows super-Eddington episodes occur which lead to rapid BH growth.
The upper limit from the integrated X-ray emission \citep{2013ApJ...778..130T} is denoted by red triangles.
The total BH mass density should be dominated by abundant low mass BHs, which is not comprised in our quasar host halos.
In this sense, our BHs which result in observable quasars at $z\sim 6$ are a biased population.

%
\if0
\begin{equation}
 \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh.
\end{equation}
%
%as a function of redshift.
Varying the minimum mass as $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$,
we find that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
%
\begin{equation}
\rho_\bullet(z)
%= \rho_{\bullet 0}\cdot e^{k_{\rm M}(z-6)}
\simeq \rho_{\bullet,0}~ 10^{k_{\rm M}(z-6)},
\end{equation}
%
where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{QLF_rhoz.png}
\caption{
{\it Left panel}: quasar luminosity functions at $z=6-10$. 
The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
evaluated by the integration of the QLF shown in the left panel.
The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
}
\label{fig:QLF_rhoz}
\vspace{5mm}
\end{figure*}

\subsection{Quasar luminosity function}
\label{sec:qlfglf}
Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
% Also, you could compare your results with Aaron Yung's results.}
In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

%On the other hand, the statistics of BH masses together with the ERDF in their growth history can rebuild quasar luminosity functions across cosmic time,
%which is interesting to be probed with future observations.
In Fig.~\ref{fig:LFs}, we divide the cosmological QLF evolution into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
The black solid and dashed curves present the QLF for the unobscured population (i.e., type-I AGNs, same as those in Fig.~\ref{fig:QLF_rhoz})
and the whole population (i.e., type-I and type-II AGNs).
The AGN obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
% sampled in \citet{2014ApJ...786..104U},
%we emphasize that the observed (Type I) QLF after the current obscuration prescription can be highly uncertain in the faint end,
%ßwhich is to be improved by the future equipments.
% More thorough studies on the high-$z$ quasar obscuration by upcoming equipments will improve the understanding on this aspect.
%We also produce the intrinsic (Type I and Type II) luminosity function without obscuration effects.
%The QLF emgerging from high redshifts quickly evolves toward brighter luminosity 
%with the number of quasars increases as BHs grow.
We also overlay the expected depths and survey volumes of upcoming near-infrared surveys by
Euclid \citep{2011arXiv1110.3193L} and RST \citep{2019arXiv190205569A}.
Only their Wide survey layers are considered here.
Table.~\ref{tab:N_detect} summarizes the coverage and limiting magnitudes in each survey,
and list the expected number of quasar detection.
Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.
The RST will be able to explore the very faint ($\Muv>-22$ mag) but abundant quasar population even at $z>10$, in principle,
after subtracting galaxy contaminants.

@@

%%%%%%%
%    Table. 2 
%%%%%%%
\startlongtable
\begin{deluxetable*}{lccccccc}%[h!]
\tablecolumns{2}
\renewcommand\thetable{2} %! fix indexing
\tablewidth{0pt} 
\tablecaption{Detection Number of Quasars Estimated for Future Surveys}
\tablehead{
  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
}
\startdata
Wide RST    &  2000 & 27   & 6758 &  1514 &  349 & 85 & 25  \\
Wide Euclid & 15000 & 24   & 6653  &  708 &   93 & -- & --  \\
\enddata
\label{tab:N_detect}
\tablecomments{
Based on the 5$\sigma$ point source detection limits, the number of quasars at each redshift are predicted
with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
}
\end{deluxetable*}

>>>>

\vspace{2mm}
%\section{Results}\label{sec:result}
\section{Results}\label{sec:fitting_result}

%\vspace{2mm}
%\subsection{Fitting Results}\label{sec:fitting_result}

@@

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=145mm]{fits_MF.png}
\caption{
The BH mass function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
For comparison, the BHMF inferred by \citetalias{2010AJ....140..546W} is overlaid (blue curve and shaded region).
The data is used for the model parameter fitting.
%.The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
% error of observation
}
\label{fig:fitmf}
\end{figure*}

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=145mm]{fits_LF.png}
\caption{
The unobscured quasar luminosity function at $z=6$ with the best-fit parameters (black solid line) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
The upper bound of faint quasar number density is derived from the cumulative QLF presented in \citet{2022NatAs...6..850J}.
The X-ray QLF data in the faint end inferred from the $z\sim 5-6.1$ quasar sample in \citet{2019ApJ...884...19G} are denoted by orange symbols,
note that we conduct an extrapolation with quasar number densities scaling with $10^{-0.72\Delta z}$ at $z$ in $5-6$ \citep{2016ApJ...833..222J}.
For comparison, we show the intrinsic QLF predicted by our model in dashed lines.
}
\label{fig:fitlf}
\vspace{2mm}
\end{figure*}

@@

%\vspace{2mm}
\section{Cosmological evolution of BH mass and quasar luminosity function}\label{sec:cosm}
%\red{KI: shall we discuss the $z$-dependence of the BHMF and QLF?
%Don't need to repeat calculations. Just using the same parameters with 1sigma scatter?
%Showing $\rho_{\bullet}(z)$ in $\Msun ~ {\rm Mpc}^{-3}$, which is the integrant of BHMF, would be interesting}

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=175mm]{BHMF_rhoz1.png}
\caption{
\if0
{\it Left panel}: BH mass functions at $z=6-10$. 
The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
evaluated by the integration of the BHMF shown in the left panel.
The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
\fi
}
\label{fig:BHMF_rhoz}
\vspace{0mm}
\end{figure*}

Based on the constraint from $z\sim 6$ quasar observations, the best-fit model from the MCMC realizations enables
us to probe the statistical aspect of BH evolution at higher redshifts.
%As a fiducial case, we take the best-fit parameters of BH growth for our $\fseed=$ 0.01 model,
%where $\tlife=18.76$ Myr, $\delta=0.055$, $\lambda_0=0.87$, and $\alpha=0.20$.
We apply the result to construct BHMFs and QLFs at $z\geq 6$ and give implications for
the future explorations of high-$z$ quasars.

\subsection{Black Hole Mass Functions}

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
for $\fseed=0.1$ (solid) and $0.01$ (dashed).
Since the mass distribution of seed BHs is already established at $M_\bullet \lesssim 2\times10^5~\Msun$ earlier on ($z\gtrsim 17$),
the high-mass tail of the BHMF is built up owing to a fraction $\fseed$ of all the seeds.
Therefore, the case with $\fseed=0.1$ yields the number of growing seeds ten times higher compared to the case with $\fseed =0.01$,
making the difference of the abundance at $M_\bullet \sim 10^{5-6}~\Msun$\footnote{
For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
For BHs with $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
the BHMFs can be characterized with a double power-law function,
similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
Toward lower redshifts, the number density of BHs in the high-mass tail increases
and SMBHs with $M_\bullet \gtrsim 10^9~\Msun$ emerge owing to efficient growth of the massive BH population.
Constrained by the \citetalias{2010AJ....140..546W} BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
the two cases produce similar shape of mass distribution in this mass and redshift range (see \S~\ref{sec:fitting_result}),
while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
%The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
%
%The different seeding fraction varies the characteristic BH mass where the BHMF slope is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see \S~\ref{sec:fitting_result}). 
% the difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see \S~\ref{sec:fitting_result}). 
%In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.

In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we present the cumulative mass density of BHs in a comoving volume
for $\fseed=0.1$ (solid) and $0.01$ (dashed),
defined by the integration of the BHMF as
%
\begin{equation}
 \rho_\bullet(z)=\int_{\mathcal{I}} \Phi_{\Mbh} (z) \Mbh ~\D \log \Mbh.
\end{equation}
%
Here, we consider three mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
and $M_\bullet \geq 10^8~\Msun$ (green).
Overall, the mass density of the heaviest BHs quickly grows toward lower redshifts,
while the mass density barely evolves for the lightest BHs.
At $z\lesssim 7-8$, more massive BHs with $\gg 10^6~\Msun$ begin to dominate the total mass budget of the entire BH population,
promoting the so-called downsizing or anti-hierarchical evolution of massive BHs 
in terms of mass occupation \citep[e.g.,][]{2014ApJ...786..104U}.
Moreover, as shown in the left panel, the mass-density evolution is affected by the choice of the seeding fraction more substantially
for less massive BHs that keep the information on their initial conditions at birth.

%%%%%%%
%    Table. 2 
%%%%%%%
%\startlongtable
\begin{deluxetable*}{lccccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{1} %! fix indexing
\tablewidth{0pt} 
\tablecaption{Detection Number of Quasars Estimated for Future Surveys}
\tablehead{
  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
}
\startdata
Wide RST    &  2000 & 27   & 6758 &  1514 &  349 & 85 & 25  \\
Wide Euclid & 15000 & 24   & 6653  &  708 &   93 & -- & --  \\
\enddata
\label{tab:N_detect}
\tablecomments{
Based on the 5$\sigma$ point source detection limits, the number of quasars at each redshift are predicted
with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
}
\end{deluxetable*}

%The mass density predicted by the $\fseed=0.1$ case is overall higher than that with $\fseed=0.01$.
%However, with $\fseed=0.01$, BHs in the low mass range quickly evolve into higher masses,
%leading to convergent results in the two cases at $z\sim 6$.
For comparison, we overlay the BH mass density evolution with $10^6<M_{\bullet}<10^8$, and $M_\bullet>10^8~\Msun$
obtained from the cosmological simulations in \citet{2022MNRAS.513..670N} (open square symbols).
At $z\lesssim 7$, our results are in overall good agreement with those simulation results.
However, our models predict more $10^{6-8}~\Msun$ BHs emerging at $z\sim 10-8$,
owing to the joint effect of our seeding and growth prescription that allows seed formation earlier on 
and (modest) super-Eddington episodes.
%the former produces BH seeds earlier than their stringent seeding criteria,
%and the latter allows super-Eddington episodes occur which lead to rapid BH growth.
Furthermore, the measured unresolved fraction of the cosmic X-ray background constrains
the global accretion history of massive BHs at $z>5$ \citep{2012A&A...545L...6S,2013ApJ...778..130T}.
Upper bounds on the accreted-mass density onto massive BHs (red triangles) prohibits overproduction of low mass BHs at cosmic dawn.
Our quasar sample in the biased, overdense region of the universe (haboring DM halos with $\Mh\gtrsim 10^{11}~\Msun$) 
are consistent with the constraint, unlike models that require a large number of stellar-mass BH remnants.

\if0
Varying the minimum mass as $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$,
we find that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
%
\begin{equation}
\rho_\bullet(z)
%= \rho_{\bullet 0}\cdot e^{k_{\rm M}(z-6)}
\simeq \rho_{\bullet,0}~ 10^{k_{\rm M}(z-6)},
\end{equation}
%
where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.

@@

\subsection{Quasar Luminosity Functions}
\label{sec:qlfglf}

\if0
Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
% Also, you could compare your results with Aaron Yung's results.}
In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
\fi

Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model.
%On the other hand, the statistics of BH masses together with the ERDF in their growth history can rebuild quasar luminosity functions across cosmic time,
%which is interesting to be probed with future observations.
In Fig.~\ref{fig:LFs}, we divide the cosmological QLF evolution into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
The black solid and dashed curves present the QLF for the unobscured population (i.e., type-I AGNs, same as those in Fig.~\ref{fig:QLF_rhoz})
and the whole population (i.e., type-I and type-II AGNs).
The AGN obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
% sampled in \citet{2014ApJ...786..104U},
%we emphasize that the observed (Type I) QLF after the current obscuration prescription can be highly uncertain in the faint end,
%ßwhich is to be improved by the future equipments.
% More thorough studies on the high-$z$ quasar obscuration by upcoming equipments will improve the understanding on this aspect.
%We also produce the intrinsic (Type I and Type II) luminosity function without obscuration effects.
%The QLF emgerging from high redshifts quickly evolves toward brighter luminosity 
%with the number of quasars increases as BHs grow.
We also overlay the expected depths and survey volumes of upcoming near-infrared surveys by
Euclid \citep{2011arXiv1110.3193L} and RST \citep{2019arXiv190205569A}.
Only their Wide survey layers are considered here.
Table.~\ref{tab:N_detect} summarizes the coverage and limiting magnitudes in each survey,
and list the expected number of quasar detection.
Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.
The RST will be able to explore the very faint ($\Muv>-22$ mag) but abundant quasar population even at $z>10$, in principle,
after subtracting galaxy contaminants.

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure}
\centering
%\includegraphics[width=160mm]{QLF_rhoz.png}
\includegraphics[width=80mm]{M0r8_f2QLF.png}
\caption{
{\it Left panel}: quasar luminosity functions at $z=6-10$. 
The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
evaluated by the integration of the QLF shown in the left panel.
The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
}
\label{fig:QLF_rhoz}
\vspace{5mm}
\end{figure}

In Fig.~\ref{fig:QLF_rhoz}, we present the quasar number density as a function of redshift for 
the case of $\fseed =0.1$ (solid) and $0.01$ (dashed).
Each curve corresponds to the value at each UV magnitude from $\Muv=-27$ mag to $-23$ mag.
Our theoretical predictions are shown at $z\geq 6$ (thick curves), while observational results are compiled at lower redshifts (thin curves).
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$,
\red{
where $k_{\rm L}\approx ***$ and $***$ for the brightest and faintest population
at $z\gtrsim 6$, respectively.
}
Observationally, a rapid decay of the quasar number density toward higher redshifts is found by previous studies
\citep[e.g.,][]{2001AJ....122.2833F,2013ApJ...768..105M,2016ApJ...833..222J,2019ApJ...884...30W},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
% Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
% suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.

%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.
